---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```

# SCOT

<!-- badges: start -->
[![R-CMD-check](https://github.com/CCBR/SCOT/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CCBR/SCOT/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

R package development for frequently used single cell RNA-seq functions

## Installation

You can install the development version of SCOT from [GitHub](https://github.com/CCBR/SCOT) with:

``` r
# install.packages("devtools")
devtools::install_github("CCBR/SCOT", dependences = TRUE)
```

## Usage

<!--
Please see the [introductory vignette](https://ccbr.github.io/SCOT/articles/intro.html)
for a quick start tutorial. -->
Take a look at the [reference documentation](https://ccbr.github.io/SCOT/reference/index.html)
for detailed information on each function in the package.

<!--
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SCOT)
## basic example code
```

-->


## Help & Contributing

Come across a **bug**? Open an [issue](https://github.com/CCBR/SCOT/issues) and include a minimal reproducible example.

Have a **question**? Ask it in [discussions](https://github.com/CCBR/SCOT/discussions).

Want to **contribute** to this project? Check out the [contributing guidelines](.github/CONTRIBUTING.md).
